\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-27 syntax.tex
resolve comments

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu'~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= ...~|~\bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma\\
    \text{Terms}   \quad & t, t_1, t_2    &&= ...~|~"W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t
  \end{alignat*}
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}
  \end{align*}
\caption{Extended Judgement forms, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgement. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

$$ 
\Rule[name=Sig Proj Beta]
{\goodSig{\Gamma}{\sigma}{n} 
\quad \goodType{\Gamma}{A}{}
\quad \goodSeal{\Gamma}{f}{\sigma}{A}
\quad \goodType{\Gamma, A}{T}{i}}
{\goodSig{\Gamma}{p_1\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv \sigma}{n}
\\ \goodType{\Gamma}{p_1\nu' \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv A}{}
\\ \goodSeal{\Gamma}{p_f\nu \  (\nu^+ \ \sigma \ \{f\} \ T) \equiv f}{\sigma}{A}
\\ \goodType{\Gamma, p_1\nu' \ \sigma}{p_2\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv T}{}
}\YZ{p_f nu' or p_f nu? In the syntax figure, you only have p_f nu, I think.}\EDJreply{p_f nu, I don't have p_f nu' here. the prime is just for specifying we are taken out the abstraction result.}
$$

@@

For notation clarity, we will sometimes use $sf'$ to emphasize that we
consider that the seal $\goodSeal{\Gamma}{s}{\sigma}{A}$ as a term
$\goodTerm{\Gamma, \cC \sigma}{sf'~s}{A[\pi_1]}$.\YZ{sf' seems unnecessary, since sf' s ad s are the same?}\EDJreply{Yes. Technically it is pretty unnecessary. It is just a bit weird to have $\goodTerm{\Gamma, \cC \sigma}{s}{A[\pi_1]}$ and $\goodSeal{\Gamma}{s}{\sigma}{A}$ at the same time because it is one derivation but turns out to be two judgements, for intrinsically typed. I can also remove ``sf'' if you don't find it weird. I initially having ``sf'' to just *emphasize* ``sf s'' should be considered as a term  and ``s'' a sealing}\YZreply{
  I'm still confused about the difference among s, sf s and sf' s.
  I thought s and sf' s were technically the same; they are both terms of type A[pi1] in a context that contains cC sigma.
  I thought sf s was different because it is a substitution.
}\EDJreply{You are absolutely right. s and sf' s are techincally the same. sf s is a substitution.
  About s and sf' s, I can say that, I don't allow something like $\goodSeal{\Gamma}{sf'~s}{\sigma}{A}$. The reason I don't allow it is only notational consideration. 
  I mean technically we can consider them the same. I can just remove all the appearances of sf' if you want and find it less confusing.
}
Notation "sf"
(used in \ruleref{Compile}) is defined as the substitution $\goodSub{\Gamma,
\cC \sigma}{(sf~s) := (\pi_1, sf'~s)}{\Gamma, A}$.

>>>>

\begin{figure}[!htb]
  \begin{alignat*}{3}
    \text{Inductive Type Signature}   \quad & \tau       &&= w\cdot~|~w^+~\tau~A~B~|~\tau[\gamma] \\
    \text{Linkage Signature}          \quad & \sigma       &&= \nu\cdot~|~\nu^+~\sigma~\{f\}~T~|~\sigma[\gamma]~|~p_1\nu~\sigma \\
    \text{Seal}          \quad & f       &&= t~|~p_f\nu~\sigma\\    
    \text{Types}   \quad & A, B, T        &&= ...~|~\bW \tau~|~\pi_1^j~|~\pi_2^j~|~\cL\sigma~|~\cC\sigma~|~p_1\nu'~\sigma~|~p_2\nu~\sigma\\
    \text{Terms}   \quad & t, t_1, t_2    &&= ...~|~"W"~T~|~"Wsup"~T~t_1~t_2~|~\mu\cdot~|~\mu^+~t~\{f\}~T~|~p_1\mu~t~|~p_2\mu~t~|~\cCt~t
  \end{alignat*}
\caption{Overview of Instrinsically-typed Syntax for extended MLTT}
\end{figure}
\begin{figure}[!htb]
  \begin{align*}
&\sigma~:~"Sig"~\Gamma~n&&\mathboxtext{\goodSig{\Gamma}{\sigma}{n}}  &&\tau~:~"WSig"~\Gamma~n&&\mathboxtext{\goodWSig{\Gamma}{\tau}{n}} \\ &h~:~"Inh"~\Gamma~\sigma_1~\sigma_2&&\mathboxtext{\goodInh{\Gamma}{h}{\sigma}{\tau}} && f~:~"Seal"~\Gamma~\sigma~T&&\mathboxtext{\goodSeal{\Gamma}{f}{\sigma}{A}}
  \end{align*}
\caption{Extended Judgement forms, as Agda types}
\end{figure}
\begin{figure}[!htb]
  \begin{minipage}[b]{0.3\linewidth}
      $$
      \Rule[name=Sig]
      {\goodCtx{\Gamma}{i} \quad n \in \nat}
      {\goodSig{\Gamma}{\_}{n} \text{ is well-formed}}
      $$
      $$
      \Rule[name=Seal]
      {\goodCtx{\Gamma}{i} \quad \goodSig{\Gamma}{\sigma}{n} 
      \quad \goodType{\Gamma}{A}{} }
      {\goodSeal{\Gamma}{\_}{\sigma}{A} \text{ is well-formed}}
      $$\YZ{Doesn't the left column show well-formedness rules for ONLY TWO of the four new judgments? Besides, are these rules used anywhere in the following? Seems a bit unusual to have well-formedness rules for judgments per se.}\EDJreply{Yes. Right column show all the well-formedness rule for all the judgement. That is unusual because it is a direct translation from QIIT. }
  \end{minipage}
  \begin{minipage}[b]{0.6\linewidth}
    \begin{minted}[]{agda}
      data Sig  : Con → ℕ → Set
      data WSig : Con → ℕ → Set 
      data Inh  : (Γ : Con) → Sig Γ n → Sig Γ m → Set
      Seal : (Γ : Con) → Sig Γ n → Sig Γ n → Set
    \end{minted}
  \end{minipage}

@@

$$ 
\Rule[name=Sig Proj Beta]
{\goodSig{\Gamma}{\sigma}{n} 
\quad \goodType{\Gamma}{A}{}
\quad \goodSeal{\Gamma}{f}{\sigma}{A}
\quad \goodType{\Gamma, A}{T}{i}}
{\goodSig{\Gamma}{p_1\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv \sigma}{n}
\\ \goodType{\Gamma}{p_1\nu' \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv A}{}
\\ \goodSeal{\Gamma}{p_f\nu \  (\nu^+ \ \sigma \ \{f\} \ T) \equiv f}{\sigma}{A}
\\ \goodType{\Gamma, p_1\nu' \ \sigma}{p_2\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv T}{}
}
$$

@@

For notation clarity, we will sometimes use $sf'$ to emphasize that we
consider that the seal $\goodSeal{\Gamma}{s}{\sigma}{A}$ as a term
$\goodTerm{\Gamma, \cC \sigma}{sf'~s}{A[\pi_1]}$.\YZ{sf' seems unnecessary, since sf' s ad s are the same?}\EDJreply{Yes. Technically it is pretty unnecessary. It is just a bit weird to have $\goodTerm{\Gamma, \cC \sigma}{s}{A[\pi_1]}$ and $\goodSeal{\Gamma}{s}{\sigma}{A}$ at the same time because it is one derivation but turns out to be two judgements, for intrinsically typed. I can also remove ``sf'' if you don't find it weird. I initially having ``sf'' to just *emphasize* ``sf s'' should be considered as a term  and ``s'' a sealing}\YZreply{
  I'm still confused about the difference among s, sf s and sf' s.
  I thought s and sf' s were technically the same; they are both terms of type A[pi1] in a context that contains cC sigma.
  I thought sf s was different because it is a substitution.
}\EDJreply{You are absolutely right. s and sf' s are techincally the same. sf s is a substitution.
  About s and sf' s, I can say that, I don't allow something like $\goodSeal{\Gamma}{sf'~s}{\sigma}{A}$. The reason I don't allow it is only notational consideration. 
  I mean technically we can consider them the same. I can just remove all the appearances of sf' if you want and find it less confusing.
}\YZreply{Yes, sf' is confusing to me.}
Notation "sf"
(used in \ruleref{Compile}) is defined as the substitution $\goodSub{\Gamma,
\cC \sigma}{(sf~s) := (\pi_1, sf'~s)}{\Gamma, A}$.
